---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `{costoffice}`

The `costoffice` package contains functions enabling the user to access the latest __Physician Office Visit Costs__ datasets from [Data.CMS.gov](https://data.cms.gov/provider-data/search?page-size=50&theme=Physician%20office%20visit%20costs). 

There are 83 datasets in total, each representing a different medical specialty. 

Broken down by ZIP code, they contain the:

  * Most Utilized HCPCS Level II Procedure Code (for both New and Established patients)
  * Price Medicare Paid for the Visit (Min-Mode-Max)
  * Copay the Patient Paid for the Visit (Min-Mode-Max)


<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Code Size](https://img.shields.io/github/languages/code-size/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice)
[![Last Commit](https://img.shields.io/github/last-commit/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice/commits/main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/costoffice/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/costoffice?branch=main)
<!-- badges: end -->


## Installation

You can install the development version of `costoffice` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/costoffice", build_vignettes = TRUE)
```
``` r
# install.packages("remotes")
remotes::install_github("andrewallenbruce/costoffice", build_vignettes = TRUE)
```

```{r echo=TRUE}
library(costoffice)
```

## `search_datasets()`

Returns a data frame of each dataset's medical specialty, date of most recent release, and a download link for it's corresponding csv file:

```{r}
# Call with no arguments to return the entire data frame
search_datasets()
```

<br>

If needed, there are two arguments to this function. Use the `specialty` argument to return only _exact_ matches (note the underscore in the names):

```{r}
search_datasets(specialty = "emergency_medicine")
```

<br>

Use the `keyword` argument to return _partial_ matches:

```{r}
search_datasets(keyword = "medicine")
```
<br>

> Return a vector of the exact names of the medical specialties by simply calling `search_datasets()$specialty`:

<br>

```{r details, echo = FALSE}
search_datasets()$specialty |> 
  details::details(summary = 'Available Medical Specialties')
```

<br>

## Example: Analyzing the `Family Practice` Specialty Dataset

```{r}
url <- search_datasets(specialty = "family_practice") |> 
  dplyr::pull(csv_url)

url
```

<br>

```{r}
fam_pract <- costoffice:::tidyup(file = url, name = "Family Practice")
```


```{r}
# Established Patient Price
fam_pract |> 
  dplyr::filter(cost == "Price") |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", c(patient, cost, hcpcs), sep = " ") |> 
  dplyr::group_by(type) |> 
  skimr::skim(dplyr::where(is.numeric)) |> 
  dplyr::select(!c(n_missing, complete_rate)) |> 
  dplyr::filter(type == "Established Price (99214)")
```

<br>

```{r}
# New Patient Price
fam_pract |> 
  dplyr::filter(cost == "Price") |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", c(patient, cost, hcpcs), sep = " ") |> 
  dplyr::group_by(type) |> 
  skimr::skim(dplyr::where(is.numeric)) |> 
  dplyr::select(!c(n_missing, complete_rate)) |> 
  dplyr::filter(type == "New Price (99203)")
```

<br>

```{r}
# Established Patient Copay
fam_pract |> 
  dplyr::filter(cost == "Copay") |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", c(patient, cost, hcpcs), sep = " ") |> 
  dplyr::group_by(type) |> 
  skimr::skim(dplyr::where(is.numeric)) |> 
  dplyr::select(!c(n_missing, complete_rate)) |> 
  dplyr::filter(type == "Established Copay (99214)")
```

<br>

```{r, message=FALSE}
# New Patient Copay
fam_pract |> 
  dplyr::filter(cost == "Copay") |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", c(patient, cost, hcpcs), sep = " ") |> 
  dplyr::group_by(type) |> 
  skimr::skim(dplyr::where(is.numeric)) |> 
  dplyr::select(!c(n_missing, complete_rate)) |> 
  dplyr::filter(type == "New Copay (99203)")
```


```{r eval=FALSE, echo=FALSE}
# Averages by State
fam_pract |> 
  dplyr::filter(cost == "Price") |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", c(patient, cost, hcpcs), sep = " ") |> 
  dplyr::filter(!is.na(state)) |> 
  dplyr::group_by(type, state) |> 
  dplyr::summarise(count_zipcodes = dplyr::n(),
                   avg_min = round(mean(min, na.rm = TRUE), 2),
                   avg_mode = round(mean(mode, na.rm = TRUE), 2),
                   avg_max = round(mean(max, na.rm = TRUE), 2),
                   avg_rng = round(mean(range, na.rm = TRUE), 2),
                   .groups = "drop") |> 
  dplyr::arrange(dplyr::desc(avg_mode))
```

<br>

<details><summary>Code</summary>

```{r}
library(ggplot2)
library(cmapplot)
p <- fam_pract |> 
  dplyr::filter(cost == "Price") |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", c(patient, cost, hcpcs), sep = " ") |> 
  ggplot(aes(x = mode, 
             color = type, 
             fill = type)) + 
  cmapplot::theme_cmap(gridlines = "h", 
                       axisticks = "x",
                       panel.grid.major.y = element_line(color = "light gray")) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(n.breaks = 5) +
  cmapplot::cmap_fill_discrete("governance") +
  cmapplot::cmap_color_discrete("governance") +
  guides(fill = guide_legend(reverse = TRUE),
         color = "none")
```

</details>

```{r fig.width=9.25, fig.height=5.5, fig.align='center', echo=FALSE}
cmapplot::finalize_plot(
  plot = p,
  title = "Price Medicare Paid Per Visit, 2022.",
  caption = "<b>Specialty:</b> Family Medicine. <br><br>
  <b>Source</b>: Centers for Medicaid & Medicare.",
  sidebar_width = 2.4,
  caption_align = 1)
```


```{r fig.width=7, fig.height=10, fig.align='center', message=FALSE}
fam_pract |> 
  dplyr::filter(cost == "Price") |> 
  dplyr::filter(!is.na(state)) |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", 
               c(patient, cost, hcpcs), 
               sep = " ") |> 
  ggplot() + 
  cmapplot::theme_cmap(gridlines = "h", 
                       axisticks = "x",
                       panel.grid.major.y = element_line(color = "light gray")) +
  stat_summary(aes(x = mode, y = forcats::fct_reorder(state, mode, median)),
    fun.min = min,
    fun.max = max,
    fun = median) +
  labs(title = "Amount Medicare Paid Per Visit: Family Medicine",
       subtitle = "Graph Shows the Range and Median of the Mode Amounts",
       x = NULL, 
       y = NULL)
```

<details><summary>Code</summary>

```{r fig.width=7, fig.height=10, fig.align='center', message=FALSE}
p2 <- fam_pract |> 
  dplyr::filter(cost == "Price") |> 
  dplyr::filter(!is.na(state)) |> 
  dplyr::mutate(hcpcs = paste0("(", hcpcs, ")")) |> 
  tidyr::unite("type", 
               c(patient, cost, hcpcs), 
               sep = " ") |> 
  ggplot() + 
  cmapplot::theme_cmap(gridlines = "h", 
                       axisticks = "x",
                       panel.grid.major.y = element_line(color = "light gray")) +
  stat_summary(aes(x = mode, y = forcats::fct_reorder(state, mode, median)),
    fun.min = min,
    fun.max = max,
    fun = median)
```

</details>

```{r fig.width=9.25, fig.height=5.5, fig.align='center', echo=FALSE}
cmapplot::finalize_plot(
  plot = p2,
  title = "Price Medicare Paid Per Visit, 2022.",
  caption = "<b>Specialty:</b> Family Medicine. <br><br>
  <b>Source</b>: Centers for Medicaid & Medicare.",
  sidebar_width = 2.4,
  caption_align = 1)
```

## Code of Conduct

Please note that the `costoffice` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/costoffice/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
