---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `costoffice`

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Code Size](https://img.shields.io/github/languages/code-size/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice)
[![Last Commit](https://img.shields.io/github/last-commit/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice/commits/main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/costoffice/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/costoffice?branch=main)
<!-- badges: end -->

<br>

## Installation

You can install the development version of `costoffice` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/costoffice")
```
``` r
# install.packages("remotes")
remotes::install_github("andrewallenbruce/costoffice")
```

<br>

## Retrieve Dataset Info

```{r echo=TRUE}
library(costoffice)
```

<br>

To retrieve information on all of the data sets (83 specialties in total), 
simply call `search_datasets()` with no arguments:


```{r}
search_datasets()
```

<br>

Search specialties by keyword:

```{r}
search_datasets(keyword = "medicine")
```


<br>

If you're searching for one in particular, just supply the `specialty` argument:

```{r}
search_datasets(specialty = "cardiac surgery") |> tidytable::glimpse()
```

<br>

## Downloading A Dataset

Each dataset has approximately 43k rows and is roughly 4.5 to 5 MB.

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  tidytable::slice_sample(n = 10) |> 
  knitr::kable()
```

<br>

## Geocoding with `zipcodeR`

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  tidytable::slice_sample(n = 10) |> 
  use_zipcoder() |> 
  knitr::kable()
```

<br>

## Summary Statistics by State

Current average prices by state for a **New Patient** office visit to a **Vascular Surgeon**:

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(specialty, 
                    state, 
                    tidytable::starts_with("new_")) |> 
  tidytable::summarise(avg_price_mode = round(mean(new_price_mode), 2),
                       avg_copay_mode = round(mean(new_copay_mode), 2),
                       .by = c(specialty, 
                               state, 
                               new_code)) |> 
  tidytable::drop_na() |> 
  knitr::kable()
```

<br>

Current average prices by state for an **Established Patient** office visit to a **Cardiologist**:

```{r}
est_cardio <- search_datasets(specialty = "cardiology") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(specialty, 
                    state, 
                    tidytable::starts_with("est_")) |> 
  tidytable::summarise(
    avg_price_min = round(mean(est_price_min), 2),
    avg_price_mode = round(mean(est_price_mode), 2),
    avg_price_max = round(mean(est_price_max), 2),
    avg_copay_min = round(mean(est_copay_min), 2),
    avg_copay_mode = round(mean(est_copay_mode), 2),
    avg_copay_max = round(mean(est_copay_min), 2),
                       .by = c(specialty, 
                               state, 
                               est_code)) |> 
  tidytable::drop_na()

est_cardio |> knitr::kable()
```


<br>

```{r}
p1 <- ggplot2::ggplot(est_cardio, 
        ggplot2::aes(forcats::fct_reorder(state, 
                                          avg_price_mode, 
                                          median),
                                          avg_price_mode)) + 
  ggplot2::geom_pointrange(
    ggplot2::aes(ymin = avg_price_min, 
                 ymax = avg_price_max), 
    size = 0, 
    colour = "darkgray", 
    linewidth = 1) +
  ggplot2::geom_point(color = "red", size = 3) +
  ggplot2::geom_point(shape = "circle open", size = 5, color = "red") +
  ggplot2::coord_flip() +
  ggplot2::scale_y_continuous(labels = scales::label_dollar()) +
  ggplot2::labs(
    x = "", 
    y = "Minimum, Mode, Maximum",
    title = "",
    subtitle = "Price Ranges by State") +
  ggplot2::theme_light()
```

<br>

```{r}
p2 <- ggplot2::ggplot(est_cardio, ggplot2::aes(forcats::fct_reorder(state, 
                                          avg_copay_mode, 
                                          median),
                                          avg_copay_mode)) + 
  ggplot2::geom_pointrange(ggplot2::aes(ymin = avg_copay_min, 
                 ymax = avg_copay_mode)) +
  ggplot2::coord_flip() +
  ggplot2::scale_y_continuous(labels = scales::label_dollar()) +
  ggplot2::labs(
    x = "", 
    y = "Average Minimum to Mode",
    title = "",
    subtitle = "Copay Ranges by State") +
  ggplot2::theme_light()
```


```{r, fig.asp=2}
library(patchwork)
(p1 + p2) +
  plot_annotation(
    title = "Cardiology: Established Patient Office Visit Costs",
    caption = "Source: data.cms.gov/provider-data",
    theme = ggplot2::theme(plot.title = ggplot2::element_text(size = 16))
  )
```


## Download All Datasets

```{r}
search_datasets() |>
  dplyr::select(csv_url) |>
  dplyr::slice_head(n = 10) |> # remove to download all sets
  tibble::deframe() |>
  rlang::set_names(basename) |>
  purrr::map(download_dataset_purrr) |>
  purrr::list_rbind(names_to = "filename") |>
  tidytable::separate_wider_delim(filename,
                                  delim = ".",
                                  names = c("specialty", "ext")) |>
  tidytable::mutate(ext = NULL) |>
  use_zipcoder() |>
  tidytable::drop_na() |>
  tidytable::relocate(specialty)
```

<br>

## Download `arrow` Table Objects

```{r}
download_dataset_arrow(specialty = "addiction medicine") |> 
  use_zipcoder_arrow()
```
<br>

## Code of Conduct

Please note that the `costoffice` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/costoffice/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
