---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `{costoffice}`

The `costoffice` package contains functions enabling the user to access the latest __Physician Office Visit Costs__ datasets from [Data.CMS.gov](https://data.cms.gov/provider-data/search?page-size=50&theme=Physician%20office%20visit%20costs). 

There are 83 datasets in total, each representing a different medical specialty. Each one contains the:

  * Most Utilized Procedure Code (HCPCS Level II aka CPT code)
  * Price Medicare Paid (Minimum-Maximum-Mode)
  * Copay the Patient Paid (Minimum-Maximum-Mode)
  
by ZIP code, for new and established patients both.


<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Code Size](https://img.shields.io/github/languages/code-size/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice)
[![Last Commit](https://img.shields.io/github/last-commit/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice/commits/main)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/costoffice/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/costoffice?branch=main)
<!-- badges: end -->


## Installation

You can install the development version of `costoffice` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/costoffice", build_vignettes = TRUE)
```
``` r
# install.packages("remotes")
remotes::install_github("andrewallenbruce/costoffice", build_vignettes = TRUE)
```

```{r echo=TRUE}
library(costoffice)
```

## `search_datasets()`

Returns a data frame of each dataset's medical specialty, date of most recent release, and a download link for it's corresponding csv file:

```{r}
# Call with no arguments to return the entire data frame
search_datasets()
```

<br>

If needed, there are two arguments to this function. Use the `specialty` argument to return only _exact_ matches (note the underscore in the names):

```{r}
search_datasets(specialty = "emergency_medicine")
```

<br>

Use the `keyword` argument to return _partial_ matches:

```{r}
search_datasets(keyword = "medicine")
```
<br>

> Return a vector of the exact names of the medical specialties by simply calling `search_datasets()$specialty`:

<br>

```{r details, echo = FALSE}
search_datasets()$specialty |> 
  details::details(summary = 'Available Medical Specialties')
```

<br>

## Code of Conduct

Please note that the `costoffice` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/costoffice/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
