---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `costoffice`

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Code Size](https://img.shields.io/github/languages/code-size/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice)
[![Last Commit](https://img.shields.io/github/last-commit/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice/commits/main)
[![Codecov](https://codecov.io/gh/andrewallenbruce/costoffice/branch/main/graph/badge.svg)](https://codecov.io/gh/andrewallenbruce/costoffice)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice)
<!-- badges: end -->

<br>

## Installation

You can install the development version of `costoffice` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/costoffice")
```
``` r
# install.packages("remotes")
remotes::install_github("andrewallenbruce/costoffice")
```

<br>

## Retrieve Dataset Info

```{r echo=TRUE}
library(costoffice)
```

<br>

To retrieve information on all of the data sets (83 specialties in total), 
simply call `search_datasets()` with no arguments:


```{r}
search_datasets()
```

<br>

If you're searching for one in particular, just supply the `specialty` argument:

```{r}
search_datasets(specialty = "vascular surgery") |> dplyr::glimpse()
```

<br>

## Downloading Datasets


```{r}
vasc <- search_datasets(specialty = "vascular surgery")

dt <- data.table::fread(vasc$csv_url)

lobstr::obj_size(dt)
```

<br>

```{r}
dt <- dt |> 
  tibble::tibble() |> 
  dplyr::slice_sample(n = 25) |> 
  dplyr::select(zip_code,
                new_top_code = most_utilized_procedure_code_for_new_patient,
                new_price_min = min_medicare_pricing_for_new_patient,
                new_price_max = max_medicare_pricing_for_new_patient,
                new_price_mode = mode_medicare_pricing_for_new_patient,
                new_copay_min = min_copay_for_new_patient,
                new_copay_max = max_copay_for_new_patient,
                new_copay_mode = mode_copay_for_new_patient,
                est_top_code = most_utilized_procedure_code_for_established_patient,
                est_price_min = min_medicare_pricing_for_established_patient,
                est_price_max = max_medicare_pricing_for_established_patient,
                est_price_mode = mode_medicare_pricing_for_established_patient,
                est_copay_min = min_copay_for_established_patient,
                est_copay_max = max_copay_for_established_patient,
                est_copay_mode = mode_copay_for_established_patient)
dt
```


```{r}
library(zipcodeR)
dt |> 
  dplyr::mutate(zip_code = purrr::map_chr(.data$zip_code, zipcodeR::normalize_zip)) |>  
  dplyr::mutate(zip_info = purrr::map_df(.data$zip_code, zipcodeR::reverse_zipcode), .after = zip_code) |>
  tidyr::unnest_wider(zip_info) |> 
  dplyr::select(city = major_city, 
                county, 
                state,
                zip_code,
                lat,
                lng,
                bounds_west,
                bounds_east,
                bounds_north,
                bounds_south,
                dplyr::contains("new"),
                dplyr::contains("est")) |> 
  tidyr::nest(geo = c(lat, lng, dplyr::starts_with("bounds")))
```




## Code of Conduct

Please note that the costoffice project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/costoffice/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
