---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

# `costoffice`

<!-- badges: start -->
[![R-CMD-check](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andrewallenbruce/costoffice/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Code Size](https://img.shields.io/github/languages/code-size/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice)
[![Last Commit](https://img.shields.io/github/last-commit/andrewallenbruce/costoffice.svg)](https://github.com/andrewallenbruce/costoffice/commits/main)
[![Codecov](https://codecov.io/gh/andrewallenbruce/costoffice/branch/main/graph/badge.svg)](https://codecov.io/gh/andrewallenbruce/costoffice)
[![CodeFactor](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice/badge)](https://www.codefactor.io/repository/github/andrewallenbruce/costoffice)
[![Codecov test coverage](https://codecov.io/gh/andrewallenbruce/costoffice/branch/main/graph/badge.svg)](https://app.codecov.io/gh/andrewallenbruce/costoffice?branch=main)
<!-- badges: end -->

<br>

## Installation

You can install the development version of `costoffice` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewallenbruce/costoffice")
```
``` r
# install.packages("remotes")
remotes::install_github("andrewallenbruce/costoffice")
```

<br>

## Retrieve Dataset Info

```{r echo=TRUE}
library(costoffice)
```

<br>

To retrieve information on all of the data sets (83 specialties in total), 
simply call `search_datasets()` with no arguments:


```{r}
search_datasets() |> knitr::kable()
```


<br>

If you're searching for one in particular, just supply the `specialty` argument:

```{r}
search_datasets(specialty = "cardiac surgery") |> tidytable::glimpse()
```

<br>

## Downloading A Dataset

Each dataset has approximately 43k rows and is roughly 4.5 to 5 MB.

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  tidytable::slice_tail(n = 10)
```

<br>

## Geocoding with `zipcodeR`


```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  tidytable::slice_tail(n = 50) |> 
  use_zipcoder() |> 
  knitr::kable()
```

<br>

## Summary Statistics by State

Current average prices by state for an office visit by a **New Patient** to a **Vascular Surgeon**:

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(specialty, 
                    state, 
                    tidytable::starts_with("new_")) |> 
  tidytable::summarise(avg_price_mode = round(mean(new_price_mode), 2),
                       avg_copay_mode = round(mean(new_copay_mode), 2),
                       .by = c(specialty, 
                               state, 
                               new_code)) |> 
  tidytable::drop_na() |> 
  knitr::kable()
```

<br>

Current average prices by state for an office visit by an **Established Patient** to a **Cardiologist**:

```{r}
search_datasets(specialty = "cardiology") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(specialty, 
                    state, 
                    tidytable::starts_with("est_")) |> 
  tidytable::summarise(avg_price_mode = round(mean(est_price_mode), 2),
                       avg_copay_mode = round(mean(est_copay_mode), 2),
                       .by = c(specialty, 
                               state, 
                               est_code)) |> 
  tidytable::drop_na() |> 
  knitr::kable()
```

<br>


## Code of Conduct

Please note that the `costoffice` project is released with a [Contributor Code of Conduct](https://andrewallenbruce.github.io/costoffice/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
