---
title: "costoffice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{costoffice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r setup}
library(costoffice)
```

<br>

## Retrieve Dataset Info with `search_datasets()`

<br>

`search_datasets()` retrieves information on the 83 data sets, separated by physician specialty. If you're searching for one specialty in particular, just supply the `specialty` argument:

<br>

```{r}
search_datasets(specialty = "cardiac surgery") |> 
  tidytable::glimpse()
```

<br>

The result contains three dates related to the last time the data was updated and the download link for the csv file.

<br>

To retrieve information on all of the data sets (83 specialties in total), 
simply call `search_datasets()` with no arguments:

<br>

```{r}
search_datasets() |> knitr::kable()
```

<br>

## Downloading A Dataset

<br>
`costoffice` uses Mark Fairbanks' excellent `tidytable` package underneath the hood (with it using `data.table` under it's hood), resulting in much smaller download sizes and lightning fast data operations.

<br>

Each individual data set has approximately 43k rows and is roughly between 4.5 to 5 MB on disk/in memory.

<br>

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  tidytable::slice_tail(n = 10)
```


<br>

## Geocoding with `zipcodeR`

<br>

`costoffice` includes a subset of zip code data from Gavin Rozzi's amazing `zipcodeR` package:

<br>

```{r}
data("zipcode_db")
zipcode_db |> 
  tidytable::slice_head() |> 
  knitr::kable()
```

<br>

Putting `use_zipcoder()` in the pipe chain will add this information to the data table:

<br>


```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  tidytable::slice_tail(n = 10) |> 
  use_zipcoder() |> 
  tidytable::select(-geo) |> 
  knitr::kable()
```


<br>

## Summary Statistics by State

<br>

Current average prices by state for an office visit by a **New Patient** to a **Vascular Surgeon**:

<br>

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(state, tidytable::starts_with("new_")) |> 
  tidytable::summarise(avg_min = mean(new_price_min),
                       avg_max = mean(new_price_max),
                       avg_mode = mean(new_price_mode),
                       avg_copay_min = mean(new_copay_min),
                       avg_copay_max = mean(new_copay_max),
                       avg_copay_mode = mean(new_copay_mode),
                       .by = c(state, new_top_code)) |> 
  knitr::kable()
```


<br>

Current average prices by state for an office visit by an **Established Patient** to a **Cardiologist**:

<br>

```{r}
search_datasets(specialty = "cardiology") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(state, tidytable::starts_with("est_")) |> 
  tidytable::summarise(avg_min = mean(est_price_min),
                       avg_max = mean(est_price_max),
                       avg_mode = mean(est_price_mode),
                       avg_copay_min = mean(est_copay_min),
                       avg_copay_max = mean(est_copay_max),
                       avg_copay_mode = mean(est_copay_mode),
                       .by = c(state, est_top_code)) |> 
  knitr::kable()
```


<br>
