---
title: "costoffice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{costoffice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r setup}
library(costoffice)
```

<br>

## Motivation

The `costoffice` package contains functions enabling the user to access the latest __Physician Office Visit Costs__ datasets from [Data.CMS.gov](https://data.cms.gov/provider-data/search?page-size=50&theme=Physician%20office%20visit%20costs). 

There are 83 datasets in total, each representing a different medical specialty. Each one contains the:

  * Most Utilized Procedure Code (HCPCS Level II aka CPT code)
  * Minimum/Maximum/Mode Price Medicare Paid
  * Minimum/Maximum/Mode Copay the Patient Paid
  
by zip code, for new and established patients both.

<br>
