---
title: "costoffice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{costoffice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = FALSE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 300, 
  out.width = "100%",
  fig.path  = "man/figures/README-"
)
```

```{r setup}
library(costoffice)
```

<br>

## Retrieve Dataset Info with `search_datasets()`

<br>

`search_datasets()` retrieves information on the 83 data sets, separated by physician specialty. If you're searching for one specialty in particular, just supply the `specialty` argument:

<br>

```{r}
search_datasets(specialty = "cardiac surgery") |> 
  tidytable::glimpse()
```

<br>

The result contains three dates related to the last time the data was updated and the download link for the csv file.

<br>

To retrieve information on all of the data sets (83 specialties in total), 
simply call `search_datasets()` with no arguments:

<br>

```{r}
search_datasets()
```

<br>

The 83 available specialties are as follows:

```{r}
search_datasets()$specialty
```

<br><br>

## Downloading A Dataset

<br>
`costoffice` uses Mark Fairbanks' excellent `tidytable` package underneath the hood (with it using `data.table` under it's hood), resulting in much smaller download sizes and lightning fast data operations.

<br>

Each individual data set has approximately 43k rows and is roughly 8 MB on disk/in memory.

<br>

```{r}
cardio <- search_datasets(specialty = "cardiology") |> 
  download_dataset()
```


```{r}
lobstr::obj_size(cardio)
```


<br>


```{r}
cardio |> 
  tidytable::slice_sample(n = 10) |> 
  knitr::kable()
```

<br><br>


## Geocoding with `zipcodeR`

<br>

`costoffice` includes a subset of zip code data from Gavin Rozzi's amazing `zipcodeR` package:

<br>

```{r}
data("zip_db")
zip_db |> tidytable::slice_head()
```

<br>

Putting `use_zipcoder()` in the pipe chain will add this information to the data table:

<br>


```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  tidytable::slice_sample(n = 10) |> 
  use_zipcoder() |> 
  knitr::kable()
```


<br><br>

## Summary Statistics by State

<br>

Current average prices & copays by state for an office visit by a **New Patient** to a **Vascular Surgeon**:

<br>

```{r}
search_datasets(specialty = "vascular surgery") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(specialty, 
                    state, 
                    tidytable::starts_with("new_")) |> 
  tidytable::summarise(avg_price_mode = round(mean(new_price_mode), 2),
                       avg_copay_mode = round(mean(new_copay_mode), 2),
                       .by = c(specialty, 
                               state, 
                               new_code)) |> 
  tidytable::drop_na() |> 
  knitr::kable()
```


<br>

Current average prices & copays by state for an office visit by an **Established Patient** to a **Cardiologist**:

<br>

```{r}
search_datasets(specialty = "cardiology") |> 
  download_dataset() |> 
  use_zipcoder() |> 
  tidytable::select(specialty, 
                    state, 
                    tidytable::starts_with("est_")) |> 
  tidytable::summarise(avg_price_mode = round(mean(est_price_mode), 2),
                       avg_copay_mode = round(mean(est_copay_mode), 2),
                       .by = c(specialty, 
                               state, 
                               est_code)) |> 
  tidytable::drop_na() |> 
  knitr::kable()
```


<br><br>
